Response to the defense feedback

### 2021-06-03 Chapter-1/Chapter-1.tex
Updates from Overleaf

Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes. Figure~\ref{fig:secret:cf} shows an example. Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6. An attacker can retrieve some information by observing the execution control-flow.

@@

Secret-dependent data accesses happen when values of secret data affect which memory location the code reads or writes. Figure~\ref{fig:secret:da} shows an example. \textsf{FSb} is an array. Depending on the value of \textsf{secret}, the code may read or write different items in the array.

>>>>

Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes. Figure~\ref{fig:secret:cf} shows an example. Depending on the value of \textsf{secret}, the code may or may not execute line 6. An attacker can retrieve some information by observing the execution control-flow.

@@

Secret-dependent data accesses happen when the value of secret data affect which memory cell the code reads or writes. Figure~\ref{fig:secret:da} shows an example. \textsf{FSb} is an array. Depending on the value of \textsf{secret}, the code may read or write different items in the array.
